### 2015-12-01 paper.tex
Address Budi's first comment about Re definition

Sandia National Laboratories, in collaboration with the US Department of Energy
developed the Reference Model devices to provide modeling targets for advancing
marine hydrokinetic (MHK) energy technology \cite{Neary2014}. The Reference
Model 2 (RM2), a cross-flow turbine intended for river environments, was
initially designed by Barone et al. \cite{Barone2011} using the CACTUS vortex
line code \cite{Murray2011}. A scaled physical model of the RM2 was then
designed and built by the Saint Anthony Falls Laboratory (SAFL) to validate the
CACTUS predictions. Experimental performance measurements were significantly
lower than the numerical results \cite{Hill2014}, which was assumed to be a 
result of the physical model's low Reynolds number
\begin{equation}
Re_L = \frac{UL}{\nu},
\label{eq:Re}
\end{equation}\textbf{\textit{[why not go straight with defining ReD and ReC here, so it's also clear which U and L are used for each of these?]}}
where $U$ is ?free-stream? velocity, $L$ is characteristic length scales (?blade-chord length?), and $\nu$ is the fluid
kinematic viscosity.

>>>>

Sandia National Laboratories, in collaboration with the US Department of Energy
developed the Reference Model devices to provide modeling targets for advancing
marine hydrokinetic (MHK) energy technology \cite{Neary2014}. The Reference
Model 2 (RM2), a cross-flow turbine intended for river environments, was
initially designed by Barone et al. \cite{Barone2011} using the CACTUS vortex
line code \cite{Murray2011}. A scaled physical model of the RM2 was then
designed and built by the Saint Anthony Falls Laboratory (SAFL) to validate the
CACTUS predictions. Experimental performance measurements were significantly
lower than the numerical results \cite{Hill2014}, which was assumed to be a 
result of the physical model's low Reynolds number
\begin{equation}
Re_D = \frac{U_\infty D}{\nu},
\label{eq:Re}
\end{equation}
where $U_\infty$ is the free stream velocity, $D$ is the rotor diameter (note
that in some cases the blade chord length $c$ is used as this length scale), and
$\nu$ is the fluid kinematic viscosity.
